Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
Add code for dispersion/dispersal measures

animalTraj %>% 
  ggplot(., aes(x = xloc, y=yloc)) +
  geom_path() +
  geom_point(data=seed_loc, aes(x = xloc, y = yloc))

>>>>

# Calculate the mean location of seeds
x_m <- mean(seed_loc$xloc)
y_m <- mean(seed_loc$yloc)
mean_dispersal <- mean(seed_loc$dispersal)
se_dispersal <- sd(seed_loc$dispersal)/sqrt(length(seed_loc$dispersal))

# Calculate seed dispersion
xi <- (x_m - seed_loc$xloc)^2
yi <- (y_m - seed_loc$yloc)^2
seed_dispersion <- sum(sqrt(xi + yi))/length(seed_loc$time)

animalTraj %>% 
  ggplot(., aes(x = xloc, y=yloc)) +
  geom_path() +
  geom_point(data=seed_loc, aes(x = xloc, y = yloc)) +
  geom_point(aes(x = x_m, y = y_m), color = "Red") + # Mean location of seeds
